Automated Topic Naming

### 2011-09-06 ese/ese.tex
dates

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, to control for differences in functional, rather than non-functional, requirements. 
We used three different open-source, partially-commercial database systems:
\begin{itemize}
\item  MySQL 3.23. Started in 1994 and MySQL 3.23 was released in early 2001. MySQL contains $320,000$ lines of C and C++ source code~\footnote{generated
using David A. Wheeler's \emph{SLOCCount},
{http://dwheeler.com/sloccount}.}. We used MySQL 3.23 history from July
31st, 2000 to August 9th 2004.
\item MaxDB 7.500. Started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project
has over $940,000$ lines of C source
code~\footnote{{http://www.sdn.sap.com/irj/sdn/maxdb}}. 
 We used MaxDB 7.500 history from June
29th, 2004 to June 19th 2006.
\item PostgreSQL 7.3. Started in the 1980s as a Berkeley research
  project~\footnote{{http://www.postgresql.org/docs/7.3/static/}}. PostgreSQL
  7.3 contains $306,000$ lines of C code.
 We used PostgreSQL 7.3 history from May 9th, 2002 to 
 August 26th 2004.

>>>>

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, to control for differences in functional, rather than non-functional, requirements. 
We used three different open-source, partially-commercial database systems:
\begin{itemize}
\item  MySQL 3.23. Started in 1994 and MySQL 3.23 was released in early 2001. MySQL contains $320,000$ lines of C and C++ source code~\footnote{generated
using David A. Wheeler's \emph{SLOCCount},
{http://dwheeler.com/sloccount}.}. We used the MySQL 3.23 version control  history from July
31st, 2000 to August 9th, 2004.
\item MaxDB 7.500. Started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project
has over $940,000$ lines of C source
code~\footnote{{http://www.sdn.sap.com/irj/sdn/maxdb}}. 
 We used the MaxDB 7.500 version control history from June
29th, 2004 to June 19th, 2006.
\item PostgreSQL 7.3. Started in the 1980s as a Berkeley research
  project~\footnote{{http://www.postgresql.org/docs/7.3/static/}}. PostgreSQL
  7.3 contains $306,000$ lines of C code.
 We used the PostgreSQL 7.3 version control  history from May 9th, 2002 to 
 August 26th, 2004.
